Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-02-22 paper/main.tex
revised the synthetic experiment description.  now we benchmark the generic ALM algorithm for the 1st benchmark

The first experiment is designed to compare the two implementations of PALM
that solve a single large instance of the $\ell_1$-minimization problem (Algorithm \ref{alg:alm_rec}) by
comparing the amount of time to solve a problem given a generic random matrix $A$ and a random sparse
vector $\xx_0$.  
The measurement $d \times n$ matrix $A$ was generated as a random Gaussian matrix, with each entry
randomly generated from the standard normal and normalized with unit norm.  The ratio of $d:n$ varied from
$10:1$ to $10:5$ with the dimension of $d$ of matrix $A$ varying from 500 to 8000.
The ground truth signals, $\xx_0$ and $\yy_k$ had a sparsity rate of 0.1 with elements generated using the standard normal and normalized with unit norm.
Because the ground truth signal $\xx_0$ and $yy_k$ are known, the algorithm terminates
when $norm(\bx-\bx_0) < tolerance$.
The measurement vector was generated with the equation $\y_0 = A \x_0 + \y_k$.   
We also varied the different inner and tolerance levels from 1e-3 to 1e-6.
We averaged the the time taken for the ALM algorithm to solve 10 instances of a problem.

>>>>

The first experiment is designed to compare the two implementations of PALM
that solve a single large instance of the $\ell_1$-minimization problem (Algorithm \ref{alg:alm}) by
comparing the amount of time to solve a problem given a generic random matrix $A$ and a random sparse
vector $\xx_0$.  
The measurement $d \times n$ matrix $A$ was generated as a random Gaussian matrix, with each entry
randomly generated from the standard normal and normalized with unit norm.  The ratio of $d:n$ varied from
$10:1$ to $10:5$ with the dimension of $d$ of matrix $A$ varying from 500 to 8000.
The ground truth signals, $\xx_0$ had a sparsity rate of 0.1 with elements generated using the standard normal and normalized with unit norm.
Because the ground truth signal $\xx_0$ is known, the algorithm terminates
when $norm(\bx-\bx_0) < tolerance$.
The measurement vector was generated with the equation $\y_0 = A \x_0$.   
We also varied the different inner and tolerance levels from 1e-3 to 1e-6.
We averaged the the time taken for the ALM algorithm to solve 10 instances of a problem.
